Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-07-26 main_paper.tex
Merge kernel and bandwidth assumptions
This commit modifies the 'background' section by moving the kernel
assumptions to the bandwidth definition. As it's currently written,
the kernel discussion is a bit out of place.

Assumption~\ref{A3} specifies the properties of the kernel functions, which are usually assumed by in the literature (see CCT).
\begin{assumption}[Kernel]\label{A3}
  For some $\kappa>0$, the kernel function $k(\cdot):[0, \kappa]\mapsto \mathbb{R}$ is bounded and nonnegative, zero outside its support, positive and continuous on $(0, \kappa)$.
\end{assumption}

This allows for the vast majority kernel functions commonly used by practitioners. Note that different kernel functions could be used for the baseline estimate, say using the linear model, and the higher order estimation used to determine the bias correction, say using a quadratic model. For simplicity, in the following discussion we use the same function for all steps of estimation.
Potentially different kernel functions could also be used for estimation below and above the cutoff. We follow CCT's notation in setting $K(\cdot)=k(-u)\1[u<0]+k(u)\1[u \geq 0]$.

For this model, if $h$ represents a bandwidth parameter, the estimator of
$\tau$, $\hat\tau(h)$, is defined as
\begin{equation*}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation*}
with
\begin{align*}
  \hat {\mu}_{+}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} K_{h}(X_{i})
\intertext{and}
  \hat {\mu}_{-}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{X_{i}<0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} K_{h}(X_{i}).
\end{align*}
where $ K_{h}(u)=\frac{1}{h}K\left( \frac{u}{h}\right)$ with $K(\cdot)$ a kernel function.

@@

Assumption~\ref{A2} specifies the bandwidth conditions assumed by CCT, which we
will also use in this paper.
\begin{assumption}[Bandwidth]\label{A2}
  Let $h$ be the bandwidth used to estimate the local linear model and let
  $b$ be the bandwidth used to estimate a second local quadratic model. Then
  $n h \to \infty$, $n b \to \infty$, $n h^{5} b^{2} \to 0$, and
  $n b^{5} h^{2} \to 0$ as $n \to \infty$.\footnote{Unless otherwise stated, all limits in this paper are assumed to hold as
    $n \to \infty$.}

\end{assumption}

@@

Under Assumptions~\ref{A1}--\ref{A3} the procedure described by
Algorithm~\ref{Alg1} provides a consistent estimator of the bias component that
converges fast enough in probability that it can be be used as a correction. As
is standard in the bootstrap literature, we will assume that the number of
bootstrap replications, $B_{1}$, is large enough that the simulation error can
be ignored. Theorem~\ref{T1} presents the result formally.

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1}--\ref{A3},
\begin{equation}
  \label{eq:4}
  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V'(h, b)^{1/2}}
  \to^{d} N(0,1),
\end{equation}
where $\Delta^*(h,b)$ is defined by Equation~\ref{eq:9}.
\end{theorem}

@@

\begin{theorem}\label{T2}
  Under Assumptions~\ref{A1}--\ref{A3},
  \begin{gather*}
    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V'(h,b) \to^p 1
  \intertext{and}
    \sup_{x}
    \Big\rvert \Pr^*[\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^* \leq x ]
    - \Pr[\hat\tau(h) - \Delta^*(h,b) - \tau \leq x] \Big\lvert \to^p 0.
  \end{gather*}
\end{theorem}

>>>>

For this model, if $h$ represents a bandwidth parameter and $K(\cdot)$ a density
function, the estimator of $\tau$, $\hat\tau(h)$, is defined as
\begin{equation*}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation*}
with
\begin{align*}
  \hat {\mu}_{+}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} \tfrac{1}{h}K(X_{i}/h)
\intertext{and}
  \hat {\mu}_{-}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{X_{i}<0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} \tfrac{1}{h} K_{h}(X_{i}/h).
\end{align*}

@@

Assumption~\ref{A2} specifies the bandwidth and kernel conditions assumed in this
paper, which are standard in this literature.

\begin{assumption}[Bandwidth and kernel]\label{A2}
  Let $h$ be the bandwidth used to estimate the local linear model and let
  $b$ be the bandwidth used to estimate a second local quadratic model. Then
  $n h \to \infty$, $n b \to \infty$, $n h^{5} b^{2} \to 0$, and
  $n b^{5} h^{2} \to 0$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to hold as
    $n \to \infty$.}
  The kernel function $K$ is positive and continuous on the interval
  $[-\kappa,~\kappa]$ and zero outside that interval.
\end{assumption}
To simplify notation, define the scaled kernel functions
\begin{align*}
  K_h(x) &= \tfrac{1}{h} K(x/h)
\intertext{and}
  K_b(x) &= \tfrac{1}{b} K(x/b).
\end{align*}
Assumption~\ref{A2} allows for the vast majority kernel functions commonly used
in practice.  Note that different kernel functions could be used for the
treatment effect estimator and the higher order approximation used for the
bootstrap.  For simplicity, though, we use the same function for all steps of
estimation in this paper.  Potentially different kernel functions and bandwidths
could also be used for estimation below and above the cutoff, but we again focus
on the simpler case here.

@@

Under Assumptions~\ref{A1} and~\ref{A2} the procedure described by
Algorithm~\ref{Alg1} provides a consistent estimator of the bias component that
converges fast enough in probability that it can be be used as a correction. As
is standard in the bootstrap literature, we will assume that the number of
bootstrap replications, $B_{1}$, is large enough that the simulation error can
be ignored. Theorem~\ref{T1} presents the result formally.

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} and~\ref{A2},
\begin{equation}
  \label{eq:4}
  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V'(h, b)^{1/2}}
  \to^{d} N(0,1),
\end{equation}
where $\Delta^*(h,b)$ is defined by Equation~\ref{eq:9}.
\end{theorem}

@@

\begin{theorem}\label{T2}
  Under Assumptions~\ref{A1} and~\ref{A2},
  \begin{gather*}
    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V'(h,b) \to^p 1
  \intertext{and}
    \sup_{x}
    \Big\rvert \Pr^*[\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^* \leq x ]
    - \Pr[\hat\tau(h) - \Delta^*(h,b) - \tau \leq x] \Big\lvert \to^p 0.
  \end{gather*}
\end{theorem}
